---
title: Classwork 9
subtitle: "Collecting Data with Python `requests` and APIs"
date: 2026-03-06
execute: 
  eval: false
  echo: false
  warning: false
  message: false
  
from: markdown+emoji
---


```{r}
#| include: false

library(tidyverse)
library(DT)
library(reticulate)
reticulate::use_condaenv("/Users/bchoe/anaconda3", required = TRUE)
```




# Question 1
Provide a Python code to get New York City air quality surveillance data using the following API endpoint:

[https://data.cityofnewyork.us/resource/c3uy-2p5r.json](https://data.cityofnewyork.us/resource/c3uy-2p5r.json)

-	Use the following query parameter dictionary in your request, which sets the **"$limit"** to control how many rows are returned:

```{.python}
# query parameters (e.g., limit rows)
param_dict = {
    "$limit": 100   # You can increase this to get more observations
}
```


::: {.callout-tip collapse="true"}
### Show answer

```{python}
import requests
import pandas as pd

endpoint = 'https://data.cityofnewyork.us/resource/c3uy-2p5r.json'  ## API endpoint

# query parameters (e.g., limit rows)
param_dict = {
    "$limit": 100   # You can increase this to get more observations
}

response = requests.get(endpoint,
                        params= param_dict)

content = response.json() # to convert JSON response data to a dictionary/ a list of dicts


df = pd.DataFrame(content)
```

:::




<br><br>

# Question 2

Use a for-loop, `requests`, and the FRED API to retrieve two macroeconomic indicators:

1. U.S. Real GDP (`series_id` = `"GDPC1"`)
2. U.S. Unemployment Rate (`series_id` = `"UNRATE"`)

Store them into one single DataFrame called `df_all`.

The `df_all` DataFrame contains both FRED series `id`s for (1) U.S. Real GDP (`series_id` = `"GDPC1"`) and (2) U.S. Unemployment Rate (`series_id` = `"UNRATE"`), and has three columns as shown below:

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

df <- readr::read_csv('https://bcdanl.github.io/data/fred-gdp-unrate.csv')
DT::datatable(df, rownames = FALSE)
```


::: callout-note

`df_all = df_all[ ['date', 'value', 'series'] ]` means: 

- “keep only these columns, and relocate them in this order.”

:::


::: {.callout-tip collapse="true"}
### Show answer

```{python}
import requests  # to handle API requests
import pandas as pd
param_dicts = {
  'api_key': 'YOUR_API_KEY', ## Change to your own key
  'file_type': 'json',
  'series_id': 'GDPC1'    ## ID for US real GDP
}

url = "https://api.stlouisfed.org/"
endpoint = "series/observations"
api_endpoint = url + "fred/" + endpoint   # sum of strings

lst_series = ['GDPC1', 'UNRATE']
df_all = pd.DataFrame()
for val in lst_series:
    
    param_dicts['series_id'] = val
    response = requests.get(api_endpoint, 
                            params = param_dicts)

    # Convert JSON response to Python dictionary.
    content = response.json() 

    # Extract the "observations" list element.
    df = pd.DataFrame( content['observations'] )
    df['series'] = val
    
    df_all = pd.concat([df_all, df], ignore_index=True)

df_all.columns

# df[ LIST ]
df_all = df_all[ ['date', 'value', 'series'] ]


```

:::


<br><br>





# Discussion


<font size = "5">Welcome to our Classwork 9 Discussion Board! 👋 </font>


This space is designed for you to engage with your classmates about the material covered in Classwork 9.

Whether you are looking to delve deeper into the content, share insights, or have questions about the content, this is the perfect place for you.

If you have any specific questions for Byeong-Hak (**@bcdanl**) regarding the Classwork 9 materials or need clarification on any points, don't hesitate to ask here. 

All comments will be stored [here](https://github.com/bcdanl/210-spr-2026-discussion/discussions).

Let's collaborate and learn from each other!


